Validation of Visual Statistical Inference, Applied to Linear Models

### 2012-08-15 submission2_reference_updated/paper_jasa blinded.tex
submitted version after fixing reference

% Article top matter
\title{Validation of Visual Statistical Inference, Applied to Linear Models}
\author{{Mahbubul Majumder, Heike Hofmann, Dianne Cook}
\thanks{Mahbubul Majumder is a PhD student (e-mail: mahbub72@gmail.com) , Heike Hofmann is an Associate  Professor and Dianne Cook is a Professor in the Department of Statistics and Statistical Laboratory, Iowa State University, Ames, IA 50011-1210. This research is supported in part by the National Science Foundation Grant \# DMS 1007697.}}
\date{\vspace{-.7in}}
%\date{\today}  %\today is replaced with the current date
\maketitle

>>>>

% Article top matter
\title{Validation of Visual Statistical Inference, Applied to Linear Models}
%\author{{Mahbubul Majumder, Heike Hofmann, Dianne Cook}
%\thanks{Mahbubul Majumder is a PhD student (e-mail: mahbub72@gmail.com) , Heike Hofmann is an Associate  Professor and Dianne Cook is a Professor in the Department of Statistics and Statistical Laboratory, Iowa State University, Ames, IA 50011-1210. This research is supported in part by the National Science Foundation Grant \# DMS 1007697.}}
\date{\vspace{-.7in}}
%\date{\today}  %\today is replaced with the current date
\maketitle
